### 2016-05-19 2016-lrec-tyvmorph/poster.tex
a questionable colour choice
git-svn-id: https://svn.code.sf.net/p/apertium/svn/branches/papers/@68421 72bbbca6-d526-0410-a7d9-f06f51895060
some work on latex version of poster
git-svn-id: https://svn.code.sf.net/p/apertium/svn/branches/papers/@68623 72bbbca6-d526-0410-a7d9-f06f51895060

\definecolor{bordercol}{RGB}{0,0,0}
%\definecolor{headercolone}{RGB}{6,130,22}
\definecolor{headercol}{cmyk}{1,0.64,0,0.6}
%\definecolor{headercolone}{cmyk}{1,0.64,0,0.6}
%\definecolor{headercoltwo}{cmyk}{0.44,0,0.15,0.17}
%\definecolor{headercolone}{cmyk}{0.3,0,0.15,0.17}
%\definecolor{headercoltwo}{cmyk}{0.3,0,0.15,0.17}
\definecolor{iumint}{cmyk}{0.40,0,0.23,0}
\definecolor{iumidnight}{cmyk}{0.71,0.30,0.13,0.41}
\definecolor{iulimestone}{cmyk}{0.11,0.13,0.14,0.26}
%\definecolor{boxcolor}{RGB}{176,208,223}
%\definecolor{boxcolor}{cmyk}{0.3,0.08,0.08,0.1}
\definecolor{boxcolor}{cmyk}{0.2,0.03,0.03,0.1}
\definecolor{headerfontcol}{RGB}{255,255,255}
\newcommand{\hilitetwo}[1]{{\addfontfeature{Color=99333399}#1}}
\newcommand{\hiliteone}[1]{{\addfontfeature{Color=06821699}#1}}
\newcommand{\hilitegrey}[1]{{\addfontfeature{Color=77777799}#1}}
\newcommand{\hilitelightgrey}[1]{{\addfontfeature{Color=CCCCCC99}#1}}
\newcommand{\hiliteblue}[1]{{\addfontfeature{Color=44697DFF}#1}}

@@

\usepackage{fontspec}
\defaultfontfeatures{PunctuationSpace=2,Scale=MatchLowercase,Mapping=tex-text}
\newfontfeature{IPA}{+mgrk}
%\setromanfont[IPA]{FreeSerif}
%\setromanfont[IPA,Scale=0.8]{CMU Serif}
%\setromanfont[IPA]{Liberation Serif}
\setromanfont[IPA]{Linux Libertine O}
%\setromanfont[IPA]{Nimbus Roman No9 L}
\setmonofont[IPA]{DejaVu Sans Mono}
\usepackage[small,bf]{caption}
\newfontfamily\qipa[IPA,Scale=MatchLowercase]{FreeSerif}
\newfontfamily\qgmk[IPA,Scale=0.8]{CMU Serif}
\newfontfamily\litamono[IPA,Scale=0.5]{DejaVu Sans Mono}
\newfontfamily\ortamono[IPA,Scale=0.625]{DejaVu Sans Mono}
\newfontfamily\diagsans[IPA,Scale=1]{DejaVu Sans}

@@

\newcommand{\tags}[1]{\hiliteone{#1}}
\newcommand{\tag}[1]{{\ortamono \hilitegrey{<}\hiliteblue{#1}\hilitegrey{>}}}
\newcommand{\archiphon}[1]{\hilitegrey{\{}\hiliteone{#1}\hilitegrey{\}}}

@@

%\newcommand{\htwo}[1]{::: {\htwofont #1} :::}%\hrule} %\hline\\}
%\newcommand{\htwo}[1]{{\htwofont \textbf{:::#1:::}}}%\hrule} %\hline\\}
\newcommand{\htwo}[1]{{\htwofont \textbf{\dotfill{}#1\dotfill{}}}}

@@

	\begin{poster}{
		grid=false,
		%eyecatcher=false,
		borderColor=bordercol,
		headerColorOne=iumidnight,
		headerColorTwo=iumidnight,
		%headerColorOne=blue,
		headerFontColor=yellow,
		% Only simple background color used, no shading, so boxColorTwo isn't necessary
		boxColorOne=boxcolor,
		headershape=roundedright,
		headerborder=open,
		headerheight=0.07\textheight,
		%headershape=roundedright,
		%headershade=plain,
		%headerfont=\Large\textsf, %Sans Serif
		%headerfont=\Large\sf\bf,
		textborder=rectangle,
		%background=plain,
		%background=user,
		background=none,
		headerborder=open,
		boxshade=plain,
		textborder=roundedleft,
		columns=3,
	}{ %Eye Catcher, empty if option eyecatcher=false - unused
		\setlength\fboxsep{0.5em}
		\setlength\fboxrule{0pt}
		\includegraphics[angle=90,height=6.2em]{apertium5b}%\hspace{-2em}
		\includegraphics[height=5.8em]{uitlogo}\hspace{1em}
		\fbox{\includegraphics[height=5.4em]{iu_tab-crop}}
		%\hspace{2.5cm}\begin{minipage}[t]{7em}
		%	\vspace{-2cm}
		%	\noindent\\
		%	\vspace{-0.5ex}\hspace{0.105cm}
		%\end{minipage}

@@

	\headerbox{Tuvan}{name=tyvan,column=0,row=0}{
		\includegraphics[width=\textwidth]{img/tuvanmap}
	}

	\headerbox{Morphological Transducers}{name=morphtrans,below=tyvan}{
		\htwo{Morphological transducers}
		\begin{itemize}
			\item Efficient (in speed \& size) models of a language's morphology
			\item Take a surface form, and produce valid lexical form(s)
			\item Take a lexical form, and produce valid surface form(s)\vspace{-0.1ex}\\
		%\end{itemize}
		%\scalebox{0.98}{
			алдым~~~\hilitetwo{↔}~~~\texttt{ал\tag{v}\tag{tv}\tag{ifi}\tag{p1}\tag{sg}},~~\texttt{алд\tag{n}\tag{px1sg}\tag{nom}}
		%}
		\end{itemize}

		\htwo{Turkic-language transducers we've made}
		\begin{itemize}
			%\item Turkish (\hiliteone{Çöltekin, 2010 \& 2014}; \hilitetwo{Oflazer, 1994})
			%\item Crimean Tatar (\hilitetwo{Altıntaş, 2001})
			%\item Turkmen (\hilitetwo{Tantuğ et al., 2006})
			%\item Kazakh (\hilitetwo{Бекманова \& Махимов, 2013})
			%\vspace{1pt}\hfill{} \hiliteone{GPL (=free and open)}!
			%\item our Kyrgyz, Kazakh, Tatar, Kumyk:\ all \hiliteone{GPL (=free and open)}!
			\item Kyrgyz \parencite{jnwmifmt2012lrecpaper}%  (Washington et al., 2012)
			\item Tatar \& Bashkort \parencite{fmtjnwisrb2012lrecpaper} %(Tyers et al., 2012)
			\item Kazakh \parencite{isjnwfmt2013mtsummitpaper} %(Salimzyanov et al., 2013)
			\item Kumyk \parencite{jnwisfmt2014lrecpaper} %(Washington et al., 2014)
			\item ongoing work on Sakha, Tuvan, Khakas, and more!
		\end{itemize}

		\htwo{Framework:\ HFST}
		\begin{itemize}
			\item Reimplements Xerox FST formalisms ({\tt lexc} \& {\tt twol})
			\item Also provides a wrapper around popular free/open-source FST toolkits: SFST, OpenFST, and Foma
		\end{itemize}
		\htwo{Approach}
		\begin{itemize}
			\item two-level method \parencite{koskenniemi83}
			\item \textbf{morphotactics} implemented in \texttt{lexc}
			\item \textbf{morphophonology} implemented in \texttt{twol} (SPE-style rules)
			\item compiled separately; compose-intersected to single transducer\vspace{-0.1ex}\\
			алдым\hfill{}\hilitetwo{↔}\hfill{}\texttt{ал\hilitegrey{>}\archiphon{D}\archiphon{I}\hilitegrey{>}м}\hfill{}\hilitetwo{↔}\hfill{}\texttt{ал\tag{v}\tag{tv}\tag{ifi}\tag{p1}\tag{sg}}\vspace{-0.1ex}\\
			алдым\hfill{}\hilitetwo{↔}\hfill{}\texttt{алд\hilitegrey{>}\archiphon{I}м}\hfill{}\hilitetwo{↔}\hfill{}\texttt{алд\tag{n}\tag{px1sg}\tag{nom}}
		\end{itemize}

@@

	\headerbox{Example}{name=example,span=2,column=1,row=0}{

@@

		\headerbox{Ongoing and future work}{name=nedostatki,column=2,below=example}{
		\begin{itemize}
				\item Current annotation of a dependency treebank for Kazakh:\\
				a similar process that helps identify errors in morphological analyses and automatic disambiguation (constraint grammar)
				%\item Leading to
				\begin{itemize}
					\item Improved rule-based morphological disambiguation% (constraint grammar)
					\item Improved morphological analyser %for Kazakh
					\item A syntactic dependency treebank %for Kazakh
				\end{itemize}
				%\item Work on rule-based morphological disambiguation with constraint grammar
				\item Future work:
				\begin{itemize}
					\item Annotate more gold standard text in more Turkic languages
					\item Research cross-linguistic techniques for analysing Turkic
				\end{itemize}
				%\item Disambiguation, more stems, clean up transducers
				%\item Machine translation between these languages
				%\item Bring other Kypchak transducers to comparable performance:\\
				%Qaraqalpaq, Bashqort, Nogay, Crimean Tatar
				%\item Other Turkic lgs:\ Uzbek, Uyghur, Chuvash, Yakut, Tuvan, etc.
			\end{itemize}
		}

		\headerbox{Further information}{name=getting,column=1,below=results,span=2}{
			\vspace{-0.2em}
			\tikzoverlay[text width=0.8in] at (6.2in, 0.04in) {
				\includegraphics[height=0.8in]{qrcode}
			};
			\begin{itemize}
				\item Part of \textbf{Apertium Turkic} project:\ \url{http://wiki.apertium.org/wiki/Apertium\_Turkic}
				\item Transducers available \textbf{live} (\href{http://turkic.apertium.org/}{\texttt{turkic.apertium.org}}), \textbf{source code} under \hiliteone{GPL} from Apertium's SVN repo
				%\item Transducers available \textbf{live} at \href{http://turkic.apertium.org/}{\texttt{turkic.apertium.org}}
				%\item \textbf{Source code} of transducers available under \hiliteone{GPL} (free!) from Apertium's SVN repo
				%info at {\small \url{http://wiki.apertium.org/wiki/apertium-kir}}
				\item Multilingual Turkic RBMT \textbf{mailing list} (>25 subscribers):\ \texttt{apertium-turkic@lists.sourceforge.net}%\\
				%\vspace{-0.5ex}Feel free to post in any language!\\\vspace{-2.5ex}
				\item And feel free to contact the authors any time!
			\end{itemize}
			\vspace{0.3em}
		}

>>>>

\definecolor{bordercol}{RGB}{0,0,0}
%\definecolor{headercolone}{RGB}{6,130,22}
\definecolor{headercol}{cmyk}{1,0.64,0,0.6}
%\definecolor{headercolone}{cmyk}{1,0.64,0,0.6}
%\definecolor{headercoltwo}{cmyk}{0.44,0,0.15,0.17}
%\definecolor{headercolone}{cmyk}{0.3,0,0.15,0.17}
%\definecolor{headercoltwo}{cmyk}{0.3,0,0.15,0.17}
\definecolor{iumint}{cmyk}{0.40,0,0.23,0}
\definecolor{iumidnight}{cmyk}{0.71,0.30,0.13,0.41}
\definecolor{iulimestone}{cmyk}{0.11,0.13,0.14,0.26}
\definecolor{tuvagold}{cmyk}{0.0,0.2,1.0,0.0}
\definecolor{tuvablue}{cmyk}{0.57,0.23,0.0,0.1}
\definecolor{boxcolor}{RGB}{176,208,223}
%\definecolor{boxcolor}{cmyk}{0.3,0.08,0.08,0.1}
%\definecolor{boxcolor}{cmyk}{0.2,0.03,0.03,0.1}
%\definecolor{boxcolor}{cmyk}{0.57,0.23,0.0,0.1}
\definecolor{headerfontcol}{RGB}{255,255,255}
\newcommand{\hilitetwo}[1]{{\addfontfeature{Color=99333399}#1}}
\newcommand{\hiliteone}[1]{{\addfontfeature{Color=06821699}#1}}
\newcommand{\hilitegrey}[1]{{\addfontfeature{Color=77777799}#1}}
\newcommand{\hilitelightgrey}[1]{{\addfontfeature{Color=CCCCCC99}#1}}
\newcommand{\hiliteblue}[1]{{\addfontfeature{Color=44697DFF}#1}}
\newcommand{\hilitegold}[1]{{\addfontfeature{Color=tuvagold}#1}}

@@

\usepackage{fontspec}
\defaultfontfeatures{PunctuationSpace=2,Scale=MatchLowercase,Mapping=tex-text}
\newfontfeature{IPA}{+mgrk}
%\setromanfont[IPA]{FreeSerif}
%\setromanfont[IPA,Scale=0.8]{CMU Serif}
%\setromanfont[IPA]{Liberation Serif}
%\setromanfont[IPA]{Linux Libertine O}
%\setromanfont[IPA]{Linux Biolinum O}
\setromanfont[IPA,Scale=1.01]{PT Sans}
%\setromanfont[IPA]{Nimbus Roman No9 L}
\setmonofont[IPA]{DejaVu Sans Mono}
\usepackage[small,bf]{caption}
%\newfontfamily\qipa[IPA,Scale=MatchLowercase]{FreeSerif}
\newfontfamily\qipa[IPA,Scale=MatchLowercase]{FreeSans}
\newfontfamily\qgmk[IPA,Scale=0.8]{CMU Serif}
\newfontfamily\litamono[IPA,Scale=0.5]{DejaVu Sans Mono}
\newfontfamily\ortamono[IPA,Scale=0.625]{DejaVu Sans Mono}
\newfontfamily\ortaqmono[IPA,Scale=0.75]{DejaVu Sans Mono}
\newfontfamily\diagsans[IPA,Scale=1]{DejaVu Sans}

@@

\newcommand{\tags}[1]{\hiliteone{#1}}
\newcommand{\tag}[1]{{\ortaqmono \hilitegrey{<}\hiliteblue{#1}\hilitegrey{>}}}
\newcommand{\archiphon}[1]{\hilitegrey{\{}\hiliteone{#1}\hilitegrey{\}}}

@@

%\newcommand{\htwo}[1]{::: {\htwofont #1} :::}%\hrule} %\hline\\}
%\newcommand{\htwo}[1]{{\htwofont \textbf{:::#1:::}}}%\hrule} %\hline\\}
%\newcommand{\htwo}[1]{{\htwofont \textbf{\hilitegold{\dotfill{}}#1\hilitegold{\dotfill{}}}}}
\newcommand{\htwo}[1]{{\htwofont \textbf{\dotfill{}#1\dotfill{}}}}
\newcommand{\dividerspace}{\vspace{0.5em}}

@@

	\begin{poster}{
		grid=false,
		%eyecatcher=false,
		borderColor=bordercol,
		headerColorOne=iumidnight,
		headerColorTwo=iumidnight,
		%headerColorOne=blue,
		headerFontColor=tuvagold,
		% Only simple background color used, no shading, so boxColorTwo isn't necessary
		boxColorOne=boxcolor,
		headershape=roundedright,
		headerborder=open,
		headerheight=0.07\textheight,
		%headershape=roundedright,
		%headershade=plain,
		%headerfont=\Large\textsf, %Sans Serif
		%headerfont=\Large\sf\bf,
		textborder=rectangle,
		%background=plain,
		%background=user,
		background=none,
		headerborder=open,
		boxshade=plain,
		textborder=roundedleft,
		columns=3,
	}{ %Eye Catcher, empty if option eyecatcher=false - unused
		\setlength\fboxsep{0.5em}
		\setlength\fboxrule{0pt}
		%\includegraphics[angle=90,height=6.2em]{apertium5b}%\hspace{-2em}
		\includegraphics[height=5.8em]{uitlogo}\hspace{1em}
		\fbox{\includegraphics[height=5.4em]{iu_tab-crop}}
		%\hspace{2.5cm}\begin{minipage}[t]{7em}
		%	\vspace{-2cm}
		%	\noindent\\
		%	\vspace{-0.5ex}\hspace{0.105cm}
		%\end{minipage}

@@

	\headerbox{Tuvan}{name=tyvan,column=0,row=0}{
		\includegraphics[width=\textwidth]{img/tuvanmap}
		\tikzoverlay[text width=1in] at (2.5in, -0in) {
			\includegraphics[width=1in]{img/Flag_of_Tuva}
		};
		\vspace{-1.2em}
		\begin{itemize}
			\item Sayan Turkic language
			\item Spoken in the Tuva Republic
			\item Approximately 300,000 speakers
			\item Agglutinative morphology
			\item Very little work on computational tools
		\end{itemize}
	}

	\headerbox{Morphological Transducers}{name=morphtrans,below=tyvan}{
		\htwo{Morphological transducers}
		\begin{itemize}
			\item Efficient (in speed \& size) models of a language's morphology
			\item Take a surface form, and produce valid lexical form(s)
			\item Take a lexical form, and produce valid surface form(s)\vspace{-0.1ex}\\
		%\end{itemize}
		%\scalebox{0.98}{
			алдым\hfill{}{\qipa \hilitetwo{↔}}\hfill{}\texttt{ал\tag{v}\tag{tv}\tag{ifi}\tag{p1}\tag{sg}},~~\texttt{алд\tag{n}\tag{px1sg}\tag{nom}}\\
			өөнде\hfill{}{\qipa \hilitetwo{↔}}\hfill{}\texttt{өг\tag{n}\tag{px3sp}\tag{loc}}
		%}
		\end{itemize}
		\dividerspace{}

		\htwo{Framework:\ HFST}
		\begin{itemize}
			\item Reimplements Xerox FST formalisms ({\tt lexc} \& {\tt twol})
			\item Also provides a wrapper around popular free/open-source FST toolkits: SFST, OpenFST, and Foma
		\end{itemize}
		\dividerspace{}

		\htwo{Approach}
		\begin{itemize}
			\item two-level method \parencite{koskenniemi83}
			\item \textbf{morphotactics} implemented in \texttt{lexc}
			\item \textbf{morphophonology} implemented in \texttt{twol} (SPE-style rules)
			\item compiled separately; compose-intersected to single transducer\vspace{-0.1ex}\\
			алдым\hfill{}{\qipa \hilitetwo{↔}}\hfill{}\texttt{ал\hilitegrey{>}\archiphon{D}\archiphon{I}\hilitegrey{>}м}\hfill{}{\qipa \hilitetwo{↔}}\hfill{}\texttt{ал\tag{v}\tag{tv}\tag{ifi}\tag{p1}\tag{sg}}\vspace{-0.1ex}\\
			алдым\hfill{}{\qipa \hilitetwo{↔}}\hfill{}\texttt{алд\hilitegrey{>}\archiphon{I}м}\hfill{}{\qipa \hilitetwo{↔}}\hfill{}\texttt{алд\tag{n}\tag{px1sg}\tag{nom}}\\
			өөнде\hfill{}{\qipa \hilitetwo{↔}}\hfill{}\texttt{өг\hilitegrey{>}\archiphon{z}\archiphon{I}\archiphon{n}\hilitegrey{>}\archiphon{D}\archiphon{A}}\hfill{}{\qipa \hilitetwo{↔}}\hfill{}\texttt{өг\tag{n}\tag{px3sp}\tag{loc}}
		\end{itemize}

@@

		\headerbox{Development cycle}{name=development,below=morphtrans}{
			\begin{tikzpicture}[xscale=1.92,yscale=2.65]%, auto]

				\node[cloud] (assumptions) at (1,2.75) {assumed generalisations};
				\node[block] (compile) at (1,2) {compile analyser};
				\node[block] (analyse) at (1,1.5) {analyse corpus};
				\node[block] (check) at (1,1) {examine freq.\ list};
				\node[decision] (missingstem) at (1,0) {missing stem?};
				\node[block] (addstem) at (0.22,2) {add stem};
				\node[decision] (phonormorph) at (2,0) {type of problem?};
				\node[block] (updatephon) at (3,0) {update phonol.};
				\node[block] (updatemorph) at (3,1) {update morphol.};
				\node[decision] (phonbetter) at( 4,0) {better?};
				\node[decision] (morphbetter) at (4,1) {better?};
				\node[cloud] (newgeneralisation) at (2.5,2) {new\\grammatical\\generalisation};

				\path[line] (assumptions) -- node [right=0.75ex, align=left, scale=\flowchartscale] {preliminary\\development} (compile);
				\path[line] (compile) -- (analyse);
				\path[line] (analyse) -- (check);
				\path[line] (check) -- node [right=0.75ex, scale=\flowchartscale, align=left] {unanalysed\\forms} (missingstem);
				\path[line] (missingstem) -| node [below=1ex, near start, scale=\flowchartscale] {yes} (addstem);
				\path[line] (addstem) -- (compile);
				\path[line] (missingstem) -- node [below=1ex, midway, scale=\flowchartscale] {no} (phonormorph);
				\path[line] (phonormorph) -- node [below=1ex, near start, scale=\flowchartscale] {phon} (updatephon);
				\path[line] (phonormorph) |- node [below=1ex, near end, scale=\flowchartscale] {morph} (updatemorph);
				\path[line] (updatephon) -- node [above=0.5ex, scale=\flowchartscale, align=center] {diff \\ freq \\ list} (phonbetter) ;
				\path[line] (updatemorph) -- node [above=0.5ex, scale=\flowchartscale, align=center] {diff \\ freq \\ list} (morphbetter) ;
				\path[line] (phonbetter.east) -- node [below=1ex, near start, scale=\flowchartscale] {yes} (4.6,0) |- (newgeneralisation.east) ;
				\path[line] (morphbetter.east) -- node [below=1ex, near start, scale=\flowchartscale] {yes} (4.6,1) |- (newgeneralisation.east) ;
				\path[line] (phonbetter.north) |- node [right=1ex, near start, scale=\flowchartscale] {no} (4,0.5) -| (updatephon.north) ;
				\path[line] (morphbetter.north) |- node [right=1ex, near start, scale=\flowchartscale] {no} (4,1.5) -| (updatemorph.north) ;
				\path[line] (newgeneralisation) -- (compile);

			\end{tikzpicture}%}

	\headerbox{Example}{name=example,span=2,column=1,row=0}{
	« Бис кожууннуң соңгукчулары-биле ажылды чорутпастай бээривиске, көргүзүглер баксыраан. »\\

		%\texttt{алд\hilitegrey{>}\archiphon{I}м}\hfill{}\hilitetwo{↔}\hfill{}\texttt{алд\tag{n}\tag{px1sg}\tag{nom}}

		\texttt{\textasciicircum Бис/бис\tag{prn}\tag{pers}\tag{p1}\tag{pl}\tag{nom}\$}\\
		\texttt{\textasciicircum кожууннуң/кожуун\tag{n}\tag{gen}\$}\\
		\texttt{\textasciicircum соңгукчулары/соңгукчу\tag{n}\tag{pl}\tag{px3sp}\tag{nom}\$}\\
		\texttt{\textasciicircum -биле/биле\tag{post}\$}\\
		\texttt{\textasciicircum ажылды/ажыл\tag{n}\tag{acc}\$}\\
		\texttt{\textasciicircum чорутпастай/чорут\tag{v}\tag{tv}\tag{cess}\tag{prc\_impf}\$}\\
		\texttt{\textasciicircum бээривиске/бер\tag{vaux}\tag{ger\_aor}\tag{px1pl}\tag{dat}\$}\\
		\texttt{\textasciicircum ,/,\tag{cm}\$}\\
		\texttt{\textasciicircum көргүзүглер/көргүзүг\tag{n}\tag{pl}\tag{nom}\$}\\
		\texttt{\textasciicircum баксыраан/баксыра\tag{v}\tag{iv}\tag{past}\tag{p3}\tag{pl}\$}\\
		\texttt{\textasciicircum ./.\tag{sent}\$}

@@

		\headerbox{Ongoing and future work}{name=nedostatki,column=2,below=example}{
		\htwo{our other Turkic-language transducers}
		\begin{itemize}
			%\item Turkish (\hiliteone{Çöltekin, 2010 \& 2014}; \hilitetwo{Oflazer, 1994})
			%\item Crimean Tatar (\hilitetwo{Altıntaş, 2001})
			%\item Turkmen (\hilitetwo{Tantuğ et al., 2006})
			%\item Kazakh (\hilitetwo{Бекманова \& Махимов, 2013})
			%\vspace{1pt}\hfill{} \hiliteone{GPL (=free and open)}!
			%\item our Kyrgyz, Kazakh, Tatar, Kumyk:\ all \hiliteone{GPL (=free and open)}!
			\item Kyrgyz \parencite{jnwmifmt2012lrecpaper}%  (Washington et al., 2012)
			\item Tatar \& Bashkort \parencite{fmtjnwisrb2012lrecpaper} %(Tyers et al., 2012)
			\item Kazakh \parencite{isjnwfmt2013mtsummitpaper} %(Salimzyanov et al., 2013)
			\item Kumyk \parencite{jnwisfmt2014lrecpaper} %(Washington et al., 2014)
			\item ongoing work on Sakha, Khakas, and more!
		\end{itemize}
		\dividerspace{}

		%\begin{itemize}

				%\item Current annotation of a dependency treebank for Kazakh:\\
				%a similar process that helps identify errors in morphological analyses and automatic disambiguation (constraint grammar)
				%%\item Leading to
				%\begin{itemize}
				%	\item Improved rule-based morphological disambiguation% (constraint grammar)
				%	\item Improved morphological analyser %for Kazakh
				%	\item A syntactic dependency treebank %for Kazakh
				%\end{itemize}
				%%\item Work on rule-based morphological disambiguation with constraint grammar
			%\end{itemize}
			\htwo{Future work}
				\begin{itemize}
					%\item Annotate more gold standard text in more Turkic languages
					%\item Research cross-linguistic techniques for analysing Turkic
					\item Dependency parsing (native and crosslingual)
					\item Increase number of stems
					\item Make more available to linguists
					\item Integrate into end-user applications (spellchecking, MT)
				\end{itemize}
				%\item Disambiguation, more stems, clean up transducers
				%\item Machine translation between these languages
				%\item Bring other Kypchak transducers to comparable performance:\\
				%Qaraqalpaq, Bashqort, Nogay, Crimean Tatar
				%\item Other Turkic lgs:\ Uzbek, Uyghur, Chuvash, Yakut, Tuvan, etc.
		}

		\headerbox{Further information}{name=getting,column=0,below=development,span=3}{
			\tikzoverlay[text height=1in] at (0in, 0.04in) {
				\includegraphics[angle=90,height=1in]{apertium5b}
			};
			%\tikzoverlay[text width=0.8in] at (6.2in, 0.04in) {
			\tikzoverlay[text height=1in] at (10in, 0.04in) {
				\includegraphics[height=1in]{qrcode}
			};
			\tikzoverlay[text height=0.5in] at (8in, 0.04in) {
				{\huge Thanks!}
			};
			\tikzoverlay[text width=6in] at (1in, 0.04in) {
			\begin{itemize}
				\item Part of \textbf{Apertium Turkic} project:\ \url{http://wiki.apertium.org/wiki/Apertium\_Turkic}
				\item Transducers available \textbf{live} on our website: {\Large \url{http://turkic.apertium.org/}} %\href{http://turkic.apertium.org/}{\texttt{turkic.apertium.org}}
				\item \textbf{Source code} under \hiliteone{GPL} from Apertium's SVN repo
				%\item Transducers available \textbf{live} at \href{http://turkic.apertium.org/}{\texttt{turkic.apertium.org}}
				%\item \textbf{Source code} of transducers available under \hiliteone{GPL} (free!) from Apertium's SVN repo
				%info at {\small \url{http://wiki.apertium.org/wiki/apertium-kir}}
				\item Multilingual Turkic RBMT \textbf{mailing list} (>25 subscribers):\ \texttt{apertium-turkic@lists.sourceforge.net}%\\
				%\vspace{-0.5ex}Feel free to post in any language!\\\vspace{-2.5ex}
				\item And feel free to contact the authors any time!
			\end{itemize}
			\vspace{0.3em}
			};
			\vspace{1in}
		}
